Supplementary material for ``An Efficient Forecasting Approach to Reduce Boundary Effects in Real-Time Time-Frequency Analysis''

### 2020-08-28 Notes/Supplementary material/SupMat.tex
sup mat

\setcounter{equation}{27}
\setcounter{figure}{7}
\setcounter{table}{3}

@@

\subsection{Preliminaries}
Recall the model~\eqref{I-eq:model.noise}. Based on the definition of matrices $\bX$ and $\bY$, we have:
\begin{align}
\dfrac1K\bX\bX^T &= \underbrace{\dfrac1K\bZ\bZ^T+\sigma^2\bI}_{\defeq S^{(0)}} + \bE^{(0)} \\
\dfrac1K\bY\bX^T &= \underbrace{\dfrac1K\bZ'\bZ^T +\sigma^2\bD}_{\defeq S^{(1)}}+ \bE^{(1)} \ ,
\end{align}
where $\bE^{(a)} := \sigma\bE_1^{(a)} + \sigma^2\bE_2^{(a)}$,
\[
\bE_1^{(a)}[m,m'] = \dfrac1K\sum_{k=0}^{K-1} \bz[N_0+m+a+k]\bw[N_0+m'+k] + \bw[N_0+m+a+k]\bz[N_0+m'+k]\ ,
\]
and
\[
\bE_2^{(a)}[m,m'] =  \dfrac1K\sum_{k=0}^{K-1} \bw[N_0+m+a+k]\bw[N_0+m'+k] - \delta_{(m+a)m'}\ ,
\]
with $a\in\{0,1\}$.
We call $\bE^{(0)}$ and $\bE^{(1)}$ {\em error matrices} because:
\begin{align*}
\EE\{\bE^{(0)}\} &= \EE\{\bE_1^{(0)}\} = \EE\{\bE_2^{(0)}\} = \bzero \\
\EE\{\bE^{(1)}\} &= \EE\{\bE_1^{(1)}\} = \EE\{\bE_2^{(1)}\} = \bzero\ .
\end{align*}
Thus, 
\begin{align*}
\bA_0 :=\bS^{(1)}{\bS^{(0)}}^\inv\,,\quad\tilde\bA := (\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\,.
\end{align*}
As a result, for $\ell\in \mathbb{N}$, 
\begin{align}
\nonumber
\bh^{(\ell)} &= \balpha^{(\ell)} - \balpha^{(\ell)}_0 \\
\nonumber
&= \be_M^T\left(\tilde\bA^\ell-\bA_0^\ell\right) \\
&= \be_M^T\left(\left((\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\right)^\ell- \bA_0^\ell\right)\ .
\label{eq:error.vec}
\end{align}

%\subsection{Study of $\bh^{(\ell)}$}
The randomness of $\bh^{(\ell)}$ completely comes from the error matrices. Besides, notice that the first $M-1$ rows in $\bE^{(1)}$ equal to the last $M-1$ rows of $\bE^{(0)}$. We gather all sources of randomness into an vector $\bg\in\RR^{M(M+1)}$, containing $M$ rows defined as
\begin{equation}
\bg = \vec\left(
\begin{bmatrix}
\bE^{(0)} \\
\be_M^T\bE^{(1)}
\end{bmatrix}
\right)\,,
\label{eq:vec}
\end{equation}
where "$\vec$" denotes the vectorization operator, concatenating the columns of a given matrix on top of one another. Then, we can write $\bh^{(\ell)}$ as $\bh^{(\ell)}=f^{(\ell)}(\bg)$ where $f^{(\ell)}$ is a deterministic function such that:
\begin{align*}
f^{(\ell)} : \RR^{M(M+1)} &\to \RR^{M} \\
 \bg &\mapsto \bh^{(\ell)}\ .
\end{align*}

\subsubsection{Study of $\bg$}
In the following, for all $r\in\{0,\ldots,M(M+1)-1\}$ we note $\bg[r] = \sigma\bg_1[r] + \sigma^2\bg_2[r]$, where 
\begin{align*}
\bg_1[r] &= \bE_1^{(a_r)}[m_r,m'_r] \\
\bg_2[r] &= \bE_2^{(a_r)}[m_r,m'_r] \ ,
\end{align*}
and $m_r,m'_r, a_r$ are the corresponding coordinates of the matrices associated with $r$ through the vectorization operation~\eqref{eq:vec}. That is why, order-two moments of this random vector is split as follows:
\begin{equation}
\bE\{\bg[r]\bg[r']\} = \sigma^2\bE\{\bg_1[r]\bg_1[r']\} + \sigma^3\bE\{\bg_1[r]\bg_2[r']\} + \sigma^3\bE\{\bg_2[r]\bg_1[r']\} + \sigma^4\bE\{\bg_1[r]\bg_1[r']\}\ .
\label{eq:gg}
\end{equation}
Then,
\begin{align}
\nonumber
\left|\bE\{\bg_1[r]\bg_1[r']\}\right| & = \bigg|\dfrac1{K^2}\EE\bigg\{\sum_{k,k'=0}^{K-1} \bz_k[m_r+a_r]\bz_{k'}[m_{r'}+a_{r'}]\bw_k[m'_r]\bw_{k'}[m'_{r'}] + \bz_k[m'_r]\bz_{k'}[m_{r'}+a_{r'}]\bw_k[m_r+a_r]\bw_{k'}[m'_{r'}] \\
\nonumber
&+ \bz_k[m_r+a_r]\bz_{k'}[m'_{r'}]\bw_k[m'_r]\bw_{k'}[m_{r'}+a_{r'}] + \bz_k[m'_r]\bz_{k'}[m'_{r'}]\bw_k[m_r+a_r]\bw_{k'}[m_{r'}+a_{r'}]\bigg\} \bigg| \\
\nonumber
& \leq \dfrac1{K^2}\left(\sum_{j=1}^J \Omega_j\right)^2 \sum_{k,k'=0}^{K-1} \EE\left\{\bw_k[m'_r]\bw_{k'}[m'_{r'}]\right\} + \EE\left\{\bw_k[m_r+a_r]\bw_{k'}[m'_{r'}]\right\} + \EE\left\{\bw_k[m'_r]\bw_{k'}[m_{r'}+a_{r'}]\right\}  \\
\nonumber
&\hspace{110pt}  + \EE\left\{\bw_k[m_r+a_r]\bw_{k'}[m_{r'}+a_{r'}]\right\} \\
\nonumber
&\leq \dfrac1{K^2}\left(\sum_{j=1}^J \Omega_j\right)^2 \sum_{k=0}^{K-1} 4 \\
&\leq \dfrac{C_\bz^2}{K}\ ,
\label{eq:g1g1}
\end{align}
where $C_\bz = 2\left(\sum_{j=1}^J \Omega_j\right)$. Besides, since odd-order moments of a zero-mean multivariate Gaussian random vector are zero, we have:
\begin{align}
\nonumber
\bE\{\bg_1[r]\bg_2[r']\} & = \dfrac1{K^2}\sum_{k,k'=0}^{K-1} \bz_k[m_r+a_r]\EE\left\{\bw_k[m'_r]\bw_{k'}[m_{r'}+a_{r'}]\bw_{k'}[m'_{r'}]\right\} + \bz_k[m'_r]\EE\left\{\bw_k[m_r+a_r]\bw_{k'}[m_{r'}+a_{r'}]\bw_{k'}[m'_{r'}]\right\}\\
\nonumber
&\hspace{30pt} - \delta_{m_{r'}+a_{r'},m'_{r'}}\bE\{\bg_1[r]\} \\
& = 0\ ,
\label{eq:g1g2}
\end{align}
Similarly,
\begin{equation}
\bE\{\bg_2[r]\bg_1[r']\} = 0\ .
\label{eq:g2g1}
\end{equation}
Besides,
\begin{align}
\nonumber
\left|\bE\{\bg_2[r]\bg_2[r']\}\right| &= \dfrac1{K^2}\bigg|\sum_{k,k'=0}^{K-1} \EE\left\{\bw_{k}[m_{r}+a_{r}]\bw_{k}[m'_{r}]\bw_{k'}[m_{r'}+a_{r'}]\bw_{k'}[m'_{r'}]\right\} - \delta_{m_{r}+a_{r},m'_{r}}\bE\{\bg_2[r']\} - \delta_{m_{r'}+a_{r'},m'_{r'}}\bE\{\bg_2[r]\}\\
\nonumber
&\hspace{30pt} + \delta_{m_{r}+a_{r},m'_{r}}\delta_{m_{r'}+a_{r'},m'_{r'}} \bigg| \\
\nonumber
&= \dfrac1{K^2} \bigg| \sum_{k,k'=0}^{K-1} \EE\left\{\bw_{k}[m_{r}+a_{r}]\bw_{k}[m'_{r}]\right\}\EE\left\{\bw_{k'}[m_{r'}+a_{r'}]\bw_{k'}[m'_{r'}]\right\} - \delta_{m_{r}+a_{r},m'_{r}}\delta_{m_{r'}+a_{r'},m'_{r'}} \\
\nonumber
&\hspace{30pt}+ \dfrac1{K^2}\sum_{k,k'=0}^{K-1}\EE\left\{\bw_{k}[m_{r}+a_{r}]\bw_{k'}[m_{r'}+a_{r'}]\right\}\EE\left\{\bw_{k}[m'_{r}]\bw_{k'}[m'_{r'}]\right\} \\
\nonumber
&\hspace{30pt}+ \dfrac1{K^2}\sum_{k,k'=0}^{K-1} \EE\left\{\bw_{k}[m_{r}+a_{r}]\bw_{k'}[m'_{r'}]\right\}\EE\left\{\bw_{k}[m'_{r}]\bw_{k'}[m_{r'}+a_{r'}]\right\} \bigg| \\
\nonumber
& \leq \dfrac1{K^2} \sum_{k=0}^{K-1} 2 \\
& \leq \dfrac2{K}\ .
\label{eq:g2g2}
\end{align}
Thus, combining results~\eqref{eq:g1g1},~\eqref{eq:g1g2},~\eqref{eq:g2g1} and~\eqref{eq:g2g2} into expression~\eqref{eq:gg} gives the following bound:
\begin{equation}
\left|\bE\{\bg[r]\bg[r']\}\right| \leq \dfrac1K \left( C_\bz^2\sigma^2 + 2 \sigma^4\right)\ .
\label{eq:gg.bound}
\end{equation}
In the same way, we show that higher-order moments behave as $o\left( \dfrac1K \right)$.

\subsubsection{Study of $f^{(\ell)}$}
In this section, we provide bounds of the first and second-order derivatives of $f^{(\ell)}$ at the origin.

Concerning the first-order derivative, from~\eqref{eq:error.vec}, we have:
\begin{align*}
\dfrac{\partial f^{(\ell)}}{\partial \bg[r]} &= \be_M^T\dfrac{\partial \tilde\bA^{\ell}}{\partial \bg[r]} \\
&= \sum_{\lambda=0}^{\ell-1} \be_M^T\tilde\bA^\lambda\dfrac{\partial \tilde\bA}{\partial \bg[r]}\tilde\bA^{\ell-1-\lambda}\ .
\end{align*}
Thus,
\begin{equation}
\nonumber
\left.\dfrac{\partial f^{(\ell)}}{\partial \bg[r]}\right|_{\bg=\bzero} = \sum_{\lambda=0}^{\ell-1} \be_M^T\bA_0^\lambda\left.\dfrac{\partial \tilde\bA}{\partial \bg[r]}\right|_{\bg=\bzero}\bA_0^{\ell-1-\lambda}\ .
\label{eq:df}
\end{equation}
Furthermore,
\begin{align*}
\dfrac{\partial \tilde\bA}{\partial \bg[r]} &= \dfrac{\partial \bE^{(1)}}{\partial \bg[r]}\left( \bS^{(0)}+\bE^{(0)}\right)^{-1} +  \left(\bS^{(1)}+\bE^{(1)}\right)\dfrac{\partial \left( \bS^{(0)}+\bE^{(0)}\right)^{-1}}{\partial \bg[r]} \\
&= \left\{
\begin{array}{ll}
\bJ_{m_r,m'_r}\left( \bS^{(0)}+\bE^{(0)}\right)^{-1} & \mbox{if}\quad a_r=1, \\
\left( (1-\delta_{m_r,0})\bJ_{m_r-1,m'_r} +\left(\bS^{(1)}+\bE^{(1)}\right)\left( \bS^{(0)}+\bE^{(0)}\right)^{-1}\bJ_{m_r,m'_r} \right) \left( \bS^{(0)}+\bE^{(0)}\right)^{-1} & \mbox{else,}
\end{array}
\right.
\end{align*}
where $\bJ_{m_r,m'_r}\in\RR^{M\times M}$ is the matrix such that $\bJ_{m_r,m'_r}[m,m'] = \delta_{m,m_r}\delta_{m',m'_r}$.
Thus,
\begin{align*}
\left.\dfrac{\partial \tilde\bA}{\partial \bg[r]}\right|_{\bg=0} &= \left\{
\begin{array}{ll}
\bJ_{m_r,m'_r}{\bS^{(0)}}^{-1} & \mbox{if}\quad a_r=1, \\
\left((1-\delta_{m_r,0})\bJ_{m_r-1,m'_r} +\bA_0\bJ_{m_r,m'_r}\right){\bS^{(0)}}^{-1} & \mbox{else.}
\end{array}
\right.
\end{align*}
Let $\|\cdot\|_\infty$ denotes the uniform norm of a vector or a matrix, \ie $\|\bM\|_\infty = \max_{n,n'} \bM[n,m']$. Then,
\begin{equation*}
\left\| \left.\dfrac{\partial \tilde\bA}{\partial \bg[r]}\right|_{\bg=0}\right\|_\infty \leq \left(1+\|\bA_0\|_\infty\right)\|{\bS^{(0)}}^{-1}\|_\infty\ .
\end{equation*}
Given equation~\eqref{eq:A0.sine}, we have 
\begin{equation}
\|\bA_0\|_\infty\leq \max\left(1,\frac{2J}{M}\right)\ ;
\label{eq:A0}
\end{equation}
and from~\eqref{eq:S0.inv}, we have that $\|{\bS^{(0)}}^{-1}\|_\infty\leq \dfrac1{\sigma^2}\left(1+\frac{2J}{M}\right)$. Then,
\begin{equation}
\left\| \left.\dfrac{\partial \tilde\bA}{\partial \bg[r]}\right|_{\bg=0}\right\|_\infty \leq \dfrac{C_{\bz,M}}{\sigma^2}\ ,
\label{eq:dA}
\end{equation}
where $C_{\bz,M}=\left(1+\max\left(1,\frac{2J}{M}\right)\right)\left(1+\frac{2J}{M}\right)$. Besides given expression~\eqref{eq:df}, for all $r\in\{0,\ldots,M(M+1)-1\}$, we have:
\begin{align*}
\left|\left.\dfrac{\partial f_m^{(\ell)}}{\partial \bg[r]}\right\vert_{\bg=\bzero}\right| &\leq d_{1,M,\ell} \|\bA_0\|_\infty^{\ell-1}\left\|\dfrac{\partial\tilde\bA}{\partial \bg[r]}\right\|_\infty\ .
\end{align*}
where $d_{1,M,\ell}$ is only depending on $M$ and $\ell$.
Therefore, given bounds~\eqref{eq:A0} and~\eqref{eq:dA}, we have:
\begin{equation}
\left|\left.\dfrac{\partial f_m^{(\ell)}}{\partial \bg[r]}\right\vert_{\bg=\bzero}\right| \leq \dfrac{d_{1,\bz,M,\ell}}{\sigma^2}\ ,
\label{eq:df.bound}
\end{equation}
where $d_{1,\bz,M,\ell}=d_{1,M,\ell}\left(1+\frac{2J}{M}\right)\left(\max\left(1,\frac{2J}{M}\right)\right)^{\ell}$.

>>>>

\setcounter{equation}{25}
\setcounter{figure}{7}
\setcounter{table}{3}

@@

\subsection{Preliminaries}

\subsubsection{Notations}
Recall the model~\eqref{I-eq:model.noise}. Based on the definition of matrices $\bX$ and $\bY$, we have:
\begin{align}
\dfrac1K\bX\bX^T &= \underbrace{\dfrac1K\bZ\bZ^T+\sigma^2\bI}_{\defeq S^{(0)}} + \bE^{(0)} \\
\dfrac1K\bY\bX^T &= \underbrace{\dfrac1K\bZ'\bZ^T +\sigma^2\bD}_{\defeq S^{(1)}}+ \bE^{(1)} \ ,
\end{align}
where $\bE^{(a)} := \sigma\bE_1^{(a)} + \sigma^2\bE_2^{(a)}$,
\[
\bE_1^{(a)}[m,m'] = \dfrac1K\sum_{k=0}^{K-1} \bz[N_0+m+a+k]\bw[N_0+m'+k] + \bw[N_0+m+a+k]\bz[N_0+m'+k]\ ,
\]
and
\[
\bE_2^{(a)}[m,m'] =  \dfrac1K\sum_{k=0}^{K-1} \bw[N_0+m+a+k]\bw[N_0+m'+k] - \delta_{(m+a)m'}\ ,
\]
with $a\in\{0,1\}$.
We call $\bE^{(0)}$ and $\bE^{(1)}$ {\em error matrices} because:
\begin{align*}
\EE\{\bE^{(0)}\} &= \EE\{\bE_1^{(0)}\} = \EE\{\bE_2^{(0)}\} = \bzero \\
\EE\{\bE^{(1)}\} &= \EE\{\bE_1^{(1)}\} = \EE\{\bE_2^{(1)}\} = \bzero\ .
\end{align*}
Thus, the matrix $\tilde\bA$, defined in equation~\eqref{I-eq:lse}, is expressed in the form:
\begin{equation*}
\tilde\bA = (\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\,.
\end{equation*}
Let $\bA_0$ denote the deterministic matrix such that $\bA_0 \defeq \bS^{(1)}{\bS^{(0)}}^\inv$. We denote by $\balpha^{(\ell)}_0$ the last row of $\bA_0^\ell$. As a result, for $\ell\in \mathbb{N}^*$, the error vector $\bh^{(\ell)}$ defined by $\bh^{(\ell)}\defeq \balpha^{(\ell)} - \balpha^{(\ell)}_0$ satisfy the equation
\begin{align}
\nonumber
\bh^{(\ell)} &= \be_M^T\left(\tilde\bA^\ell-\bA_0^\ell\right) \\
&= \be_M^T\left(\left((\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\right)^\ell- \bA_0^\ell\right)\ .
\label{eq:error.vec}
\end{align}

The randomness of $\bh^{(\ell)}$ completely comes from the error matrices. Besides, notice that the first $M-1$ rows in $\bE^{(1)}$ equal to the last $M-1$ rows of $\bE^{(0)}$. We gather all sources of randomness into a vector $\bg\in\RR^{M(M+1)}$, defined as
\begin{equation}
\bg = \vec\left(
\begin{bmatrix}
\bE^{(0)} \\
\be_M^T\bE^{(1)}
\end{bmatrix}
\right)\,,
\label{eq:vec}
\end{equation}
where "$\vec$" denotes the vectorization operator, that concatenates the columns of a given matrix on top of one another. Then, we can write $\bh^{(\ell)}$ as $\bh^{(\ell)}=f^{(\ell)}(\bg)$ where $f^{(\ell)}$ is a deterministic function such that:
\begin{align*}
f^{(\ell)} : \RR^{M(M+1)} &\to \RR^{M} \\
 \bg &\mapsto \bh^{(\ell)}\ .
\end{align*}

In the following paragraphs, we provide some useful results to prove Theorem 1.

\subsubsection{Expression of $\bA_0$}
It follows from the signal model~\eqref{I-eq:sum.sine} that matrices $\bS^{(0)}$ and $\bS^{(1)}$ take the following form:
\begin{align}
\nonumber
\bS^{(a)}[m,m'] &= \sigma^2\delta_{(m+a)m'}+\sum_{j,j'=1}^J\dfrac{\Omega_j\Omega_{j'}}{K}\sum_{k=0}^{K-1} \cos\left(2\pi \frac{f_j}{\fs}(N_0+m+a+k)+\varphi_j\right)\cos\left(2\pi \frac{f_{j'}}{\fs}(N_0+m'+k)+\varphi_{j'}\right) \\
\nonumber
&= \sigma^2\delta_{(m+a)m'}+\sum_{j=1}^J\dfrac{\Omega_j^2}{2K}\sum_{k=0}^{K-1} \cos\left(2\pi \frac{f_j}{\fs}(m+a-m')\right) + \cos\left(2\pi \frac{f_j}{\fs}(2k+m+a+m'+2N_0)\right)\\
\nonumber
&= \sigma^2\delta_{(m+a)m'}+\sum_{j=1}^J\Bigg( \dfrac{\Omega_j^2}2\cos\left(2\pi \frac{f_j}{\fs}(m+a-m')\right) + \dfrac{\Omega_j^2}{2K}\underbrace{\sum_{k=0}^{K-1}\cos\left(2\pi \frac{f_j}{\fs}(2k+m+a+m'+2N_0)\right)}_{=0\ \mathrm{because}\ \frac{f_j}\fs=\frac{p'_j}K } \Bigg)\\
&= \sigma^2\delta_{(m+a)m'}+\sum_{j=1}^J\dfrac{\Omega_j^2}2\cos\left(2\pi \frac{f_j}{\fs}(m+a-m')\right)\ .
\label{eq:S1}
\end{align}
Thus, $\bS^{(0)}$ is a circulant matrix, and is therefore diagonalizable in the Fourier basis:
\[
\bS^{(0)} = \bU\bLambda^{(0)}\bU^*\ ,
\]
where $\bU[m,m']=\frac1{\sqrt{M}}e^{-2\ii\pi mm'/M}$ and $\bLambda^{(0)} = \mathrm{diag}(\lambda_0^{(0)},\dots,\lambda_{M-1}^{(0)})$ with
\begin{align*}
\lambda_m^{(0)} &= \sigma^2 + \sum_{j=1}^J\dfrac{\Omega_j^2}2\sum_{q=0}^{M-1} \cos\left(2\pi\frac{f_j}{\fs} q\right) e^{-2\ii\pi qm/M} \\
&= \sigma^2 + \dfrac{M}{4}\sum_{j=1}^J\Omega_j^2(\delta_{m,p_j} + \delta_{m,M-p_j})\ .
\end{align*}
Therefore,
\begin{align*}
{\bS^{(0)}}^\inv  &= \bU{\bLambda^{(0)}}^\inv\bU^*\,,
\end{align*}
which leads to
\begin{equation}
{\bS^{(0)}}^\inv[m,m']  = \dfrac1{\sigma^2}\delta_{m,m'}-\dfrac{2}{M\sigma^2}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j \dfrac{m-m'}{M}\right)\,.
\label{eq:S0.inv}
\end{equation}
Consequently, combining equations~\eqref{eq:S1} and~\eqref{eq:S0.inv}, we have
\begin{align}
\nonumber
\bA_0[m,m']  &= \sum_{q=0}^{M-1} {\bS^{(1)}}[m,q]{\bS^{(0)}}^\inv[q,m'] \\
&= \delta_{m+1,m'} + \dfrac2M\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j\frac{m'}{M}\right)\delta_{m+1,M}\,.
\label{eq:A0.sine}
\end{align}

\subsubsection{Study of $\bg$}
In the following, for all $r\in\{0,\ldots,M(M+1)-1\}$ we note $\bg[r] = \sigma\bg_1[r] + \sigma^2\bg_2[r]$, where 
\begin{align*}
\bg_1[r] &= \bE_1^{(a_r)}[m_r,m'_r] \\
\bg_2[r] &= \bE_2^{(a_r)}[m_r,m'_r] \ ,
\end{align*}
and $m_r,m'_r, a_r$ are the corresponding coordinates of the matrices associated with $r$ through the vectorization operation~\eqref{eq:vec}. That is why, order-two moments of this random vector is split as follows:
\begin{equation}
\bE\{\bg[r]\bg[r']\} = \sigma^2\bE\{\bg_1[r]\bg_1[r']\} + \sigma^3\bE\{\bg_1[r]\bg_2[r']\} + \sigma^3\bE\{\bg_2[r]\bg_1[r']\} + \sigma^4\bE\{\bg_1[r]\bg_1[r']\}\ .
\label{eq:gg}
\end{equation}
Then,
\begin{align}
\nonumber
\left|\bE\{\bg_1[r]\bg_1[r']\}\right| & = \bigg|\dfrac1{K^2}\EE\bigg\{\sum_{k,k'=0}^{K-1} \bz_k[m_r+a_r]\bz_{k'}[m_{r'}+a_{r'}]\bw_k[m'_r]\bw_{k'}[m'_{r'}] + \bz_k[m'_r]\bz_{k'}[m_{r'}+a_{r'}]\bw_k[m_r+a_r]\bw_{k'}[m'_{r'}] \\
\nonumber
&+ \bz_k[m_r+a_r]\bz_{k'}[m'_{r'}]\bw_k[m'_r]\bw_{k'}[m_{r'}+a_{r'}] + \bz_k[m'_r]\bz_{k'}[m'_{r'}]\bw_k[m_r+a_r]\bw_{k'}[m_{r'}+a_{r'}]\bigg\} \bigg| \\
\nonumber
& \leq \dfrac1{K^2}\left(\sum_{j=1}^J \Omega_j\right)^2 \sum_{k,k'=0}^{K-1} \EE\left\{\bw_k[m'_r]\bw_{k'}[m'_{r'}]\right\} + \EE\left\{\bw_k[m_r+a_r]\bw_{k'}[m'_{r'}]\right\} + \EE\left\{\bw_k[m'_r]\bw_{k'}[m_{r'}+a_{r'}]\right\}  \\
\nonumber
&\hspace{110pt}  + \EE\left\{\bw_k[m_r+a_r]\bw_{k'}[m_{r'}+a_{r'}]\right\} \\
\nonumber
&\leq \dfrac1{K^2}\left(\sum_{j=1}^J \Omega_j\right)^2 \sum_{k=0}^{K-1} 4 \\
&\leq \dfrac{C_\bz^2}{K}\ ,
\label{eq:g1g1}
\end{align}
where $C_\bz \defeq 2\left(\sum_{j=1}^J \Omega_j\right)$. Besides, since odd-order moments of a zero-mean multivariate Gaussian random vector are zero, we have:
\begin{align}
\nonumber
\bE\{\bg_1[r]\bg_2[r']\} & = \dfrac1{K^2}\sum_{k,k'=0}^{K-1} \bz_k[m_r+a_r]\EE\left\{\bw_k[m'_r]\bw_{k'}[m_{r'}+a_{r'}]\bw_{k'}[m'_{r'}]\right\} + \bz_k[m'_r]\EE\left\{\bw_k[m_r+a_r]\bw_{k'}[m_{r'}+a_{r'}]\bw_{k'}[m'_{r'}]\right\}\\
\nonumber
&\hspace{30pt} - \delta_{m_{r'}+a_{r'},m'_{r'}}\bE\{\bg_1[r]\} \\
& = 0\ .
\label{eq:g1g2}
\end{align}
Similarly,
\begin{equation}
\bE\{\bg_2[r]\bg_1[r']\} = 0\ .
\label{eq:g2g1}
\end{equation}
Besides,
\begin{align}
\nonumber
\left|\bE\{\bg_2[r]\bg_2[r']\}\right| &= \dfrac1{K^2}\bigg|\sum_{k,k'=0}^{K-1} \EE\left\{\bw_{k}[m_{r}+a_{r}]\bw_{k}[m'_{r}]\bw_{k'}[m_{r'}+a_{r'}]\bw_{k'}[m'_{r'}]\right\} - \delta_{m_{r}+a_{r},m'_{r}}\bE\{\bg_2[r']\} - \delta_{m_{r'}+a_{r'},m'_{r'}}\bE\{\bg_2[r]\}\\
\nonumber
&\hspace{30pt} + \delta_{m_{r}+a_{r},m'_{r}}\delta_{m_{r'}+a_{r'},m'_{r'}} \bigg| \\
\nonumber
&= \dfrac1{K^2} \bigg| \sum_{k,k'=0}^{K-1} \EE\left\{\bw_{k}[m_{r}+a_{r}]\bw_{k}[m'_{r}]\right\}\EE\left\{\bw_{k'}[m_{r'}+a_{r'}]\bw_{k'}[m'_{r'}]\right\} - \delta_{m_{r}+a_{r},m'_{r}}\delta_{m_{r'}+a_{r'},m'_{r'}} \\
\nonumber
&\hspace{30pt}+ \dfrac1{K^2}\sum_{k,k'=0}^{K-1}\EE\left\{\bw_{k}[m_{r}+a_{r}]\bw_{k'}[m_{r'}+a_{r'}]\right\}\EE\left\{\bw_{k}[m'_{r}]\bw_{k'}[m'_{r'}]\right\} \\
\nonumber
&\hspace{30pt}+ \dfrac1{K^2}\sum_{k,k'=0}^{K-1} \EE\left\{\bw_{k}[m_{r}+a_{r}]\bw_{k'}[m'_{r'}]\right\}\EE\left\{\bw_{k}[m'_{r}]\bw_{k'}[m_{r'}+a_{r'}]\right\} \bigg| \\
\nonumber
& \leq \dfrac1{K^2} \sum_{k=0}^{K-1} 2 \\
& \leq \dfrac2{K}\ .
\label{eq:g2g2}
\end{align}
Thus, combining results~\eqref{eq:g1g1},~\eqref{eq:g1g2},~\eqref{eq:g2g1} and~\eqref{eq:g2g2} into expression~\eqref{eq:gg} gives the following bound:
\begin{equation}
\left|\bE\{\bg[r]\bg[r']\}\right| \leq \dfrac1K \left( C_\bz^2\sigma^2 + 2 \sigma^4\right)\ .
\label{eq:gg.bound}
\end{equation}
In the same way, we show that higher-order moments behave as $o\left( \dfrac1K \right)$.

\subsubsection{Study of $f^{(\ell)}$}
In this section, we provide bounds on the first and second-order derivatives of $f^{(\ell)}$ at the origin.

Concerning the first-order derivative, from~\eqref{eq:error.vec}, we have:
\begin{align*}
\dfrac{\partial f^{(\ell)}}{\partial \bg[r]} &= \be_M^T\dfrac{\partial \tilde\bA^{\ell}}{\partial \bg[r]} \\
&= \sum_{\lambda=0}^{\ell-1} \be_M^T\tilde\bA^\lambda\dfrac{\partial \tilde\bA}{\partial \bg[r]}\tilde\bA^{\ell-1-\lambda}\ .
\end{align*}
Thus,
\begin{equation}
\left.\dfrac{\partial f^{(\ell)}}{\partial \bg[r]}\right|_{\bg=\bzero} = \sum_{\lambda=0}^{\ell-1} \be_M^T\bA_0^\lambda\left.\dfrac{\partial \tilde\bA}{\partial \bg[r]}\right|_{\bg=\bzero}\bA_0^{\ell-1-\lambda}\ .
\label{eq:df}
\end{equation}
Furthermore,
\begin{align*}
\dfrac{\partial \tilde\bA}{\partial \bg[r]} &= \dfrac{\partial \bE^{(1)}}{\partial \bg[r]}\left( \bS^{(0)}+\bE^{(0)}\right)^{-1} +  \left(\bS^{(1)}+\bE^{(1)}\right)\dfrac{\partial \left( \bS^{(0)}+\bE^{(0)}\right)^{-1}}{\partial \bg[r]} \\
&= \left\{
\begin{array}{ll}
\bJ_{m_r,m'_r}\left( \bS^{(0)}+\bE^{(0)}\right)^{-1} & \mbox{if}\quad a_r=1, \\
\left( (1-\delta_{m_r,0})\bJ_{m_r-1,m'_r} +\left(\bS^{(1)}+\bE^{(1)}\right)\left( \bS^{(0)}+\bE^{(0)}\right)^{-1}\bJ_{m_r,m'_r} \right) \left( \bS^{(0)}+\bE^{(0)}\right)^{-1} & \mbox{else,}
\end{array}
\right.
\end{align*}
where $\bJ_{m_r,m'_r}\in\RR^{M\times M}$ is the matrix such that $\bJ_{m_r,m'_r}[m,m'] \defeq \delta_{m,m_r}\delta_{m',m'_r}$.
Thus,
\begin{align*}
\left.\dfrac{\partial \tilde\bA}{\partial \bg[r]}\right|_{\bg=\bzero} &= \left\{
\begin{array}{ll}
\bJ_{m_r,m'_r}{\bS^{(0)}}^{-1} & \mbox{if}\quad a_r=1, \\
\left((1-\delta_{m_r,0})\bJ_{m_r-1,m'_r} +\bA_0\bJ_{m_r,m'_r}\right){\bS^{(0)}}^{-1} & \mbox{else.}
\end{array}
\right.
\end{align*}
Let $\|\cdot\|_\infty$ denote the uniform norm of a vector or a matrix, \ie~$\|\bM\|_\infty = \max_{n,n'} \bM[n,n']$. Then,
\begin{equation*}
\left\| \left.\dfrac{\partial \tilde\bA}{\partial \bg[r]}\right|_{\bg=\bzero}\right\|_\infty \leq \left(1+\|\bA_0\|_\infty\right)\left\|{\bS^{(0)}}^{-1}\right\|_\infty\ .
\end{equation*}
Given equation~\eqref{eq:A0.sine}, we have 
\begin{equation}
\|\bA_0\|_\infty\leq \max\left(1,\frac{2J}{M}\right)\ ;
\label{eq:A0}
\end{equation}
and from~\eqref{eq:S0.inv}, we have that $\left\|{\bS^{(0)}}^{-1}\right\|_\infty\leq \dfrac1{\sigma^2}\left(1+\frac{2J}{M}\right)$. Then,
\begin{equation}
\left\| \left.\dfrac{\partial \tilde\bA}{\partial \bg[r]}\right|_{\bg=\bzero}\right\|_\infty \leq \left(1+\max\left(1,\frac{2J}{M}\right)\right)\left(1+\frac{2J}{M}\right)\dfrac{1}{\sigma^2}\ .
\label{eq:dA}
\end{equation}
Besides given expression~\eqref{eq:df}, for all $r\in\{0,\ldots,M(M+1)-1\}$, we have:
\begin{align*}
\left|\left.\dfrac{\partial f_m^{(\ell)}}{\partial \bg[r]}\right\vert_{\bg=\bzero}\right| &\leq 2M\|\bA_0^{\ell-1}\|_\infty \left\| \left.\dfrac{\partial \tilde\bA}{\partial \bg[r]}\right|_{\bg=\bzero}\right\|_\infty + M^2\sum_{\lambda=1}^{\ell-2} \|\bA_0^\lambda\|_\infty \left\| \left.\dfrac{\partial \tilde\bA}{\partial \bg[r]}\right|_{\bg=\bzero}\right\|_\infty  \|\bA_0^{\ell-1-\lambda}\|_\infty \\
&\leq \left(2 + (\ell-2)M\right)M^{\ell-1} \|\bA_0\|_\infty^{\ell-1}\left\|\left.\dfrac{\partial\tilde\bA}{\partial \bg[r]}\right|_{\bg=\bzero}\right\|_\infty\ .
\end{align*}
Therefore, given bounds~\eqref{eq:A0} and~\eqref{eq:dA}, we have:
\begin{equation}
\left|\left.\dfrac{\partial f_m^{(\ell)}}{\partial \bg[r]}\right\vert_{\bg=\bzero}\right| \leq \dfrac{d_{1,\bz,M,\ell}}{\sigma^2}\ ,
\label{eq:df.bound}
\end{equation}
where $d_{1,\bz,M,\ell}\defeq \left(2 + (\ell-2)M\right)M^{\ell-1}\left(\max\left(1,\frac{2J}{M}\right)\right)^{\ell-1}\left(1+\max\left(1,\frac{2J}{M}\right)\right)\left(1+\frac{2J}{M}\right)$.
